Measurement and Probability in Fuzzy Quantum Theories

### 2017-06-25 prop_iop.tex
prop_iop.tex \subsubsection{Sates Consistent with a QIVPM Induced by the Born Rule} Updating...
prop_iop.tex Fix spacing again...

>>>>

\subsubsection{Sates Consistent with a QIVPM Induced by the Born Rule}

Since we want to consider QIVPMs induced by the Born rule, it is easier
to work with the states instead of the probability measures, which
gives us the following definition.

\begin{definition}A state\nb$\rho$ is consistent with $\bar{\mu}$
on a projector\nb$P$ if $\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$,
i.e., $\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu}|_{\left\{ P\right\} }\right)$,
and denoted by $\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$.
Moreover, $\rho\in\coreBorn\left(\bar{\mu},S\right)$ means $\rho$
is consistent with $\bar{\mu}$ on every projector in $S$, i.e.,
$\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu}|_{S}\right)$.\end{definition}

When we work with mixed states or density matrices, we also need a
norm to compute the distance among them.

\begin{lemma}Given a Hilbert space with the set of all projectors\nb$\events$,
and an interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
with the maximum length of intervals in $\mathscr{I}$ is $1/n$.
For two mixed state\nb$\rho$ and $\rho'$, if $\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
then $\left\Vert \rho-\rho'\right\Vert \le1/n$.\end{lemma}

\begin{proof}By definition, we have
\begin{equation}\eqalign{ 
 & \rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)\\ 
\Leftrightarrow & \forall P\in\events\ \mu_{\rho}^{\mathrm{B}}\left(P\right)\in\iota\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)\\ 
\Rightarrow & \forall\textrm{ normalized pure state }\ket{\psi}\ \mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\in\iota\left(\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right) 
}\end{equation}
\end{proof}
